---
title: "Formative Assesment 2"
author: "Dwight Gonzales"
output:
  html_document:
    df_print: paged
  pdf_document: default
date: "2024-02-17"
---

# Number 2

```{r}
# Generate a random sequence
r <- sample(c("hh", "tt", "ht", "th"), 100, TRUE)

# Calculate the frequency of each outcome
f <- table(r) / 100

# Calculate the relative frequencies as percentages
p <- f * 100

# Print the generated random sequence
cat("Generated Random Sequence:\n")
cat(r, sep = ", ")

# Print the relative frequencies
cat("\nRelative Frequencies:\n")
cat(round(f, digits = 2), "\n")

# Print the relative frequencies as percentages
cat("Relative Frequencies as Percentages:\n")
cat(paste(round(p, digits = 2), "%"), "\n")

# Create a barplot
barplot(f, main = "Results for Heads and Tails", xlab = "Head and Tail", ylab = "Frequency", col = c("red", "blue", "green", "purple"), names.arg = c("hh", "tt", "ht", "th"))
```

# Number 3

```{r}
# Generate a random sequence
s = sample(c(1, 2, 3, 4, 5, 6), 600, TRUE)

# Calculate the frequency of each outcome
fr = table(s) / 600

# Calculate the relative frequencies as percentages
pr = fr * 100

# Print the generated random sequence
cat("Generated Random Sequence:")
cat(s, sep = ", ")

# Print the relative frequencies
cat("Relative Frequencies:")
cat(paste(round(fr, digits=2), "%"))

# Print the relative frequencies as percentages
cat("Relative Frequencies as Percentages:")
cat(paste(round(pr, digits=2), "%"))

# Create a barplot for the relative frequencies
barplot(fr, main = "Results for dice", xlab = "Outcomes", ylab = "Relative Frequency", col = "skyblue", names.arg = unique(s))